Downward shortwave solar irradiance enhancement by clouds.

### 2024-05-22 article/article.Rmd
Commit 2024-05-22 04:15

.............

These selections have some subjectivity, as the definition of clear sky, is depended
on the intended usage. Our main focus is to be able to identify the OIR created by the
clouds. Although, the aerosols and water vapor are always present and can not be
completely removed. 
The effect of the different clearness levels

.............

<!-- extreme cases criterion -->
Another aspect of the CE events, that is often reported in the relative bibliography,
are cases of extreme cloud enhancement (ECE). These are cases of CE where the
measured intensity of the irradiance, exceeds the equivalent TSI on the top of the
atmosphere, and satisfy the Equation\nobreakspace{}\ref{eq:ECE}.
\begin{equation}
\text{ECE}: \text{GHI}_\text{i} > \cos(\theta) \times E_{i\odot} / r_{i}^2
\label{eq:ECE}
\end{equation}
where: $\theta$ the solar zenith angle, $E_{\odot}$ the solar constant, $r$ the Sun -- Earth distance, and $i$ each of the one-minute observation.

>>>>

The definition of the CE events with this method, has a level of subjectivity. The
actual clear sky irradiance, is not known, and can only be approximated. Although,
because our main focus is to be able to identify the OIR created by the clouds, we
expect that we were able to detect all the major events of OIR due to CE.  Where,
minor enhancements may be not detected, are less significant for most of our results.

<!-- extreme cases criterion -->
Another aspect of the CE events, that is often reported in the relative bibliography,
are cases of extreme cloud enhancement (ECE). These are cases of CE, where the
measured intensity of the irradiance, exceeds the equivalent TSI on the top of the
atmosphere, and satisfy the Equation\nobreakspace{}\ref{eq:ECE}.
\begin{equation}
\text{ECE}: \text{GHI}_\text{i} > \cos(\theta) \times E_{i\odot} / r_{i}^2
\label{eq:ECE}
\end{equation}
where: $\theta$ the solar zenith angle, $E_{\odot}$ the solar constant, $r$ the Sun -- Earth distance, and $i$ each of the one-minute observation.

To give a better understanding of the CE identification procedure, we included 
an example of the CE identification for a selected day .... appendix....
where the use of the reference and the threshold are shown, along with the relevant
measurements.

Similar we provide yearly plots
